\batcave: Bayesian Analysis Tools for Context-Aware Variant Evaluation

### 2019-09-16 NAR_DRAFT.tex
small fixes

\end{verbatim}
\end{tiny}
Variants identified by MuTect are labelled as to whether they pass all MuTect filters, pass all filters *other* than the evidence threshold \textrm{tlod\_f\_star}, or fail to pass any filter other than \textrm{tlod\_f\_star}. Variants that pass all filters or fail only \textrm{tlod\_f\_star} are then passed to {method} for prior estimation and rescoring.

@@

>>>>

\end{verbatim}
\end{tiny}
Variants identified by MuTect are labelled as to whether they pass all MuTect filters, pass all filters *other* than the evidence threshold \textrm{tlod\_f\_star}, or fail to pass any filter other than \textrm{tlod\_f\_star}. 
Variants that pass all filters or fail only \textrm{tlod\_f\_star} are then passed to \batcave for prior estimation and rescoring.

@@

\section{Data Availability}
COSMIC mutation signatures version 2 is available at \footnotesize{https://cancer.sanger.ac.uk/cosmic/signatures\_v2}.
